\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-08 doc/sw-system.tex
Note on truncation of P-C curves in Figure 7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
\caption{Completeness-estimated purity curves for the \sw system, using
the \cfhtls training set.}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
\caption{Completeness-estimated purity curves for the \sw system, using
the \cfhtls training set. The curves are truncated at the high purity end by
the ``detection'' limit subject probability (subjects in the online
\StageOne analysis were
deemed to be detected at $p=0.95$, while at \StageTwo rounding error led to 
an upper limit of $p=1.0$).}
\label{fig:results:sample:CP}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
